Your Awesome Title

### 2017-11-16 Doc/respond_to_reviewer.Rmd

---
title: "Response to reviewers"
author: "Daijiang Li"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    css: ../template/respond_to_reviewer.css
    keep_md: no
    theme: readable
    toc: yes
  pdf_document:
    highlight: zenburn
    keep_tex: no
    template: ../template/respond_to_reviewer.tex
    toc: no
    toc_depth: 3
    latex_engine: xelatex
  word_document: default
---

```{r knitr_options, echo=FALSE}
library(knitr)
opts_chunk$set(fig.align='center', cache=TRUE, warning = FALSE, message = FALSE)
# load(".RData")
options(digits = 3, width = 88)

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/respond_to_reviewer.tex'
tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/respond_to_reviewer.css'
# change directory accordingly
if(!file.exists(tpl_1f <- '../template/respond_to_reviewer.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- '../template/respond_to_reviewer.css')) download.file(tpl_2, tpl_2f)
```

Dear Editors,

Thank you for your help with our manuscript. The constructive comments from reviewers and Editors have greatly improved it.

Sincerely,

Daijiang Li

>09-Nov-2017

>Dear Dr. Li

>We have now completed the review process on your manuscript ....

>You will find the reports of the referees (if any), and the comments of the handling editor, ...

>I invite you to

>Thank you again for submitting to ....

>Yours sincerely

>Editor-in-chief

----------------

### EDITOR-IN-CHIEF'S COMMENTS TO AUTHORS

--

----------------

### EDITOR'S COMMENTS TO AUTHORS

>Editor:   
>Comments to the Author:
>Dear authors

>Thanks for your resubmission, ...

>Best wishes,
>Editor...

We have added qualifiers in these subsections as suggested.

>L299 change ‘reveal’ to ‘suggest’ or ‘imply’ or similar.

Changed 'reveal' to "suggest."

### REVIEWER COMMENTS TO AUTHORS

---------------

>If there are no comments above, the reviewer may have chosen to upload a file. Please check ScholarOne Manuscripts for any attached files, which may be found at the end of the decision letter in your author centre under 'Manuscripts with decisions'.

### 2017-11-16 Doc/ms.Rmd
add responses to reviwers template

---
title: "Your Awesome Title"
author: "Author One and Author Two"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
link-citations: yes
csl: ../template/oikos.csl
bibliography: ../template/ref.bib
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align='center', cache=F, warning = FALSE, message = T, echo = FALSE)
options(digits = 3, width = 88)
```

>>>>

---
title: "Your Awesome Title"
author: "Author One and Author Two"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: ../template/ref.bib
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align='center', cache=F, warning = FALSE, message = T, echo = FALSE)
options(digits = 3, width = 88)

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/preamble.tex'
tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/doc_prefix.tex'
# bib_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/ref.bib'
# change directory accordingly
if(!file.exists(tpl_1f <- '../template/preamble.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- '../template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
```
